Verification of concurrent design patterns with data

### 2019-02-19 2018-Arch-pNets/arch-pNets.tex
intro appendices

>>>>

\add{The following appendices are included for convenience and would be integrated into a research report if the paper is accepted for publication. The first appendices gives complementary informations previously published, while the other appendices provide additional formal details complementing architecture definitions, proofs of theorems, and the case study.}
